---
title: "Crime Data"
author: "Sabrina Chok"
date: "4/5/2019"
output: html_document
---

Data: FBI: UCR Crime Data
For my final project, I hope to create informative graphics utilizing US crime data that compares crime data rates from different states, regions, and years (since 2010). I'm particularly interested in creating an interactive tool that would enable people to look at various types of crime data (violent crimes, property crimes, etc). As of right now, I've only created a graphic that looks at violent crime data, but I hope to do more animated graphics moving forward!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(ggthemes)
library(readxl)
library(maps)
library(gganimate)

```


```{r}
us_states <- map_data("state")

c10_11 <- read_xls("crime_2010_2011.xls") %>% 
  clean_names() 

c12_13 <- read_xls("crime_2012_2013.xls") %>% 
  clean_names() 

c14_15 <- read_xls("crime_2014_2015.xls") %>% 
  clean_names() 

c16_17 <- read_xls("crime2016.xls") %>% 
  clean_names() 


all <- bind_rows(c10_11, c12_13, c14_15, c16_17, .id = "dataset") %>% 
  gather(crime_type, value, c(violent_crime:rape_revised_definition_rate_per_100_000))

all_states <- all %>% filter(!area %in% c("United States Total", "Northeast", "New England", "Middle Atlantic", "Midwest", 
                                          "East North Central", "West North Central", "South", "South Atlantic", "East South Central",
                                          "West South Central", "West", "Mountain", "Pacific"))
```

```{r}

  top_ten <-  all_states %>% 
      filter(year == 2010,
        crime_type == "violent_crime_rate_per_100_000") %>% 
      arrange(desc(value)) %>% 
      slice(1:10) %>% 
      select(area) %>% 
  pull()
         

all_states_formatted <- all_states %>%
  filter(!is.na(area),
         crime_type == "violent_crime_rate_per_100_000") %>% 
  group_by(year) %>%
  # The * 1 makes it possible to have non-integer ranks while sliding
  mutate(rank = rank(-value),
         Value_rel = value/value[rank==1],
         Value_lbl = paste0(" ",round(value/1e9))) %>%
  group_by(area) %>% 
  filter(rank <=10) %>%
  ungroup()

all_states_formatted %>% 
ggplot(aes(rank, group = area, 
                fill = as.factor(area), color = as.factor(area))) +
  geom_tile(aes(y = value/2,
                height = value,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(area, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y = value,label = value, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=25, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm")) + 
        transition_states(year, transition_length = 4, state_length = 4) +
       view_follow(fixed_x = TRUE)  +
  labs(title = 'Violent Crime Rates per Year : {closest_state}',  
       subtitle  =  "Top 10 States",
       caption  = "")
  
```


```{r}
all %>% 
  filter(area %in% c("Northeast", "United States Total", "Middle Atlantic", "Midwest", "East North Central", "West North Central", "South")) %>% 
  select(area, year, violent_crime_rate_per_100_000) %>% 
  ggplot(aes(x = year, y = violent_crime_rate_per_100_000, color = area)) + geom_line() +
  xlab("Year")
```

```{r}
all %>% 
       filter(year == 2010) %>% 
       select(area, burglary_rate_per_100_000) %>% 
       gather(crime_type, value, burglary_rate_per_100_000) %>% 
       arrange(desc(value)) %>% 
       slice(1:10) 
```

```{r}
all %>%
       filter(area == "New York") %>%
       select(area, year, violent_crime_rate_per_100_000) %>% 
      gather(crime_type, y, violent_crime_rate_per_100_000)
```

```{r}

x <- all %>% 
  filter(year == "2012") %>% 
  mutate(region = tolower(area)) %>% 
  select(-year, -dataset, -population) 

y <- left_join(us_states, x)

ggplot(data = y, mapping = aes(x = long, y = lat, group = group, fill = murder_and_nonnegligent_manslaughter_rate_per_100_000)) + geom_polygon()
```

```{r}
c14_15 %>% 
  filter(year == "2014") %>% 
  select(area, year, violent_crime_rate_per_100_000) %>% 
  ggplot(aes(x = year, y = violent_crime_rate_per_100_000)) + geom_jitter() 
```


```{r echo = FALSE}

c16_17 %>% 
  filter(year == "2016",
         !is.na(area)) %>% 
  select(area, violent_crime_rate_per_100_000) %>% 
  mutate(violent_crime_rate_per_100_000 = as.numeric(violent_crime_rate_per_100_000)) %>% 
  arrange(desc(violent_crime_rate_per_100_000)) %>% 
  #slice(1:10) %>% 
  ggplot(mapping = aes(x = reorder(area, violent_crime_rate_per_100_000), y = violent_crime_rate_per_100_000)) + geom_point() + coord_flip() +
  labs(y = "Violent Crime Rate Per 100,000", 
       x = "States",
       title = "States with the Top 10 Violent Crime Rates in",
       caption = "Source: US FBI:UCR Crime Data 2016") + 
  theme_economist_white()
```

